---
title: "Practical Machine learning"
author: "Guiatin Youssouf"
date: "15 février 2016"
output: html_document
---

# Introduction

In this project write-up, I have used the data from Human Activity Recognition (HAR).
The aim was to train a model based on the data of various sensor values,
which could later be used to predict the Classe variable,
that is the manner in which the participants of HAR did the exercise.

# read data
```{r,echo=FALSE}
setwd("D:\\Biostatistique\\john hopkings\\practical machine\\project")
```
```{r,echo=TRUE}
train=read.csv("pml-training.csv",na.strings=c("","NA"))
test=read.csv("pml-testing.csv",na.strings=c("","NA"))
```
# remove missing value
```{r,echo=TRUE}
trainR=train[, colSums( is.na(train) ) < nrow(train)*0.5]
testR=test[, colSums( is.na(test) ) < nrow(test)*0.5]
```

I have realized that some columns have a lot of missing (NA) values. Instead of trying to model them,
I have decided to remove them from the data set.
So the first step, after having loaded the required caret library ,
was to detect and eliminate columns with a lot of missing values:
#suppression des 7 premières colonnes
```{r,echo=TRUE}
trainR=trainR[,-c(1:7)]
testR=testR[,-c(1:7)]
```

# create data partition
```{r,echo=TRUE}
set.seed(3433)
library(caret)
intrain=createDataPartition(trainR$classe,p=0.6,list=FALSE)

train=trainR[intrain,]
test=trainR[-intrain,]
```

# Data Modelling

```{r,echo=TRUE}

library(randomForest)

##controlRf <- trainControl(method="cv", 4)
##modelRf <- train(classe ~ ., data=train, method="rf", trControl=controlRf, ntree=500, allowParallel=TRUE)
modelRf<- readRDS("rfmodel.rds")
modelRf
```

we predict this modeling on validation data set

```{r,echo=TRUE}
predictRf <- predict(modelRf, test)
confusionMatrix(test$classe, predictRf)
```

Lets check Accuracy
```{r,echo=TRUE}
accuracy <- postResample(predictRf, test$classe)
saveRDS(modelRf, "rfmodel.RDS")
```
Accuracy of this prediction model is 99.18%.

Out of Sample Error is calculated here
```{r,echo=TRUE}
error <- 1 - as.numeric(confusionMatrix(test$classe, predictRf)$overall[1])
error
```
error

out of sample error is  0.008157023.
# Predicting for Test Data Set

Now, we apply the model to the original testing data set downloaded from the data source.
Generate "problem_id_x.txt" Files for the assignments. These generated individual
files are stored in working directory.

```{r,echo=TRUE}
 pml_write_files = function(x){
   n = length(x)
   for(i in 1:n){
     filename = paste0("problem_id_",i,".txt")
     write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
   }
 }
 #pml_write_files(predictRf)
```